---
title: "Exam With Question and their variants"
author: "Author 1, Author 2"
date: "2023/september"
output: html_document
---


To produce XML Moodle file first do knitr and check the exam. Then,

```
# Install from GitHub
devtools::install_github("https://github.com/jpcaveiro/rmdmoodle", reset=TRUE)

# Load functions
library(rmdmoodle)

# Build this exam
xmlmoodle("exam-en.Rmd")
```

This exam has one "Random Question" with 3 variants. Check "Outline" button in RStudio.


# Random Question 01 - Descriptive Statistics - CLOZE

Here, after `#`, one can write:

* code shared by all variants
* notes that will not appear in Moodle


This question has 3 variants.


```{r}
samplesize <- 5

ages = list(
  round(rnorm(samplesize, 10,2),1),
  round(rnorm(samplesize, 20,2),1),
  round(rnorm(samplesize, 30,2),1)
)
```



## Variante  `r (VAR<-1)`

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The maximum value of the sample is {:NUMERICAL:=`r max(ages[[VAR]])`}.


### feedback

Provide here some feedback.



## Variante  `r (VAR<-2)`

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The minimum value of the sample is {:NUMERICAL:=`r max(ages[[VAR]])`}.


### feedback

Provide here some feedback.



## Variante  `r (VAR<-3)`

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The value of $x_2$ is {:NUMERICAL:=`r ages[[VAR]][2]`}.


### feedback

Provide here some feedback.


