---
title: "Exam With Question and their variants"
author: "Author 1, Author 2"
date: "2023/september"
output: html_document
---


This format, called `rmdmoodle exam`, implements the following ideas:

* this file contains an exam
* an exam is made by questions marked with `# Question 01` (example below)
* each question has variants marked with `## Variant 01` (example below)
* after each variante could be a tag `### feedback` if it is necessary to give a feedback



Between the title and up until first question marked with `#`, like this note, one can write:

* code shared by all Questions and their Variants
* notes that will not appear in moodle
* one should not start lines with `#` because its reserved to declare questions and variants


Code example shared with all Questions and their Variants:
```{r}
# fix seed to debug while developing an exam
set.seed(10)
# set sample size
samplesize = 10
```


Next, it's the declaration of the first exam question.



# Question 01 - Descriptive Statistics - CLOZE

Here one can write:

* code shared by all variants
* notes that will no be in moodle

For example, this question has 3 variants.


```{r}
ages = list(
  round(rnorm(samplesize, 10,2),1),
  round(rnorm(samplesize, 20,2),1),
  round(rnorm(samplesize, 30,2),1)
)
```



## Variante  `r VAR=1 ; sprintf("%02d", VAR)`

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The maximum value of the sample is {:NUMERICAL:=`r max(ages[[VAR]])`}.


### feedback

Provide here some feedback.



## Variante  `r VAR=2 ; sprintf("%02d", VAR) `

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The minimum value of the sample is {:NUMERICAL:=`r max(ages[[VAR]])`}.


### feedback

Provide here some feedback.



## Variante  `r VAR=3 ; sprintf("%02d", VAR) `

Consider the following sample:

```{r echo=FALSE} 
cat(ages[[VAR]],'\n')
```


**(a)** 

The sample mean is {:NUMERICAL:=`r mean(ages[[VAR]])`:0.1} (round to 1 decimal place).

**(b)** 

The value of $x_2$ is {:NUMERICAL:=`r ages[[VAR]][2]`}.


### feedback

Provide here some feedback.


